---
title: "reading_data"
author: "Yu"
date: "2024-05-20"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)
library(httr)

```

## Scrape a table

I want the first table from [this
page](https://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm)


read in the html

```{r}
url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"
drug_use_html = read_html(url)

drug_use_html
```

extract the table(s); focus on the first one

```{r}
tabl_marj = 
drug_use_html %>% 
  html_nodes(css = "table") %>% 
  .[[1]] %>% 
  html_table() %>% 
  slice(-1)
```

html_nodes(css = "table"): extract the tables
.[[1]]/first(): just use the first one
html_table: converts an HTML table into a data frame
slice(-1): delete the first row


## Star Wars Movie info

I want the data form [here] (https://www.imdb.com/list/ls070150896/)

```{r}
url = "https://www.imdb.com/list/ls070150896/"

swm_html = read_html(url)
```

Grab elements that I want.

```{r}
title_vec = 
  swm_html %>% 
  html_nodes(css = ".lister-item-header a") %>% 
  html_text()

gross_rev_vec = 
  swm_html %>%
  html_elements(".text-small:nth-child(7) span:nth-child(5)") %>%
  html_text()

runtime_vec = 
  swm_html %>%
  html_elements(".runtime") %>%
  html_text()

swm_df = 
  tibble(
    title = title_vec,
    rev = gross_rev_vec,
    runtime = runtime_vec)
```

".lister-item-header a": is from Selector Gadget.
html_text: only select texts
tibble(): form a data frame


## Get some water data 

This is coming from an API

```{r}
nyc_water = 
  GET("https://data.cityofnewyork.us/resource/ia2d-e54m.csv") %>% 
  content("parsed")

nyc_water = 
  GET("https://data.cityofnewyork.us/resource/ia2d-e54m.json") %>% 
  content("text") %>% 
  jsonlite::fromJSON() %>% 
  as_tibble()
```

GET: get data from this API
content(): parse content in the data
json: another type of dataset
jsonlite::fromJSON(): parse the data


## BRFSS

Some process, different data

```{r}
brfss_2010 = 
  GET("https://chronicdata.cdc.gov/resource/acme-vg9e.csv", 
      query = list("$limit" = 5000)) %>% 
  content("parsed")
```

query = list("$limit" = 5000): default is 1000


## Some data aren't so nice

Let's look at Pokemon

```{r}
pokemon_data =
  GET("https://pokeapi.co/api/v2/pokemon/1") %>% 
  content

pokemon_data$name
pokemon_data$height
pokemon_data$abilities
```

## Closing thoughts

Be reasonable.

